---
title: "Lab2_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab2_Vignette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
runtime: shiny
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/"
)
```

```{r setup}
library(Lab2KorbDSA5403)
```

# Introduction

This vignette introduces the Lab2KorbDSA5403 package, which provides tools for
Bayesian analysis of a binomial coin‑flipping experiment when the probability of
success, $\theta$, is restricted to a discrete grid of possible values.

The package includes:

- A function coin() that computes the posterior distribution for a discrete‑theta binomial model.
- A Shiny app that interactively visualizes the prior, likelihood, and posterior.
- A wrapper function *runCoinApp()* that launches the Shiny app from within the package.

# The Discrete-Theta Coin Model

Suppose a binomial experiment is performed with:

- *n* trials
- *z* observed successes
- a discrete grid of possible values for $\theta$

The function *coin(theta, prior, n, z, alpha)* computes:

- Posterior probabilities over the grid
- Equal‑tail ($1-\alpha$) credible interval ($L,U$)
- Posterior mean
- Prior mean
- A tri‑plot overlaying the prior, likelihood, and posterior

Below is a demonstration using a uniform prior on a grid of 101 points.

```{r, fig.width=8, fig.height=5}
result <- coin(theta = seq(0,1,length = 101), prior = "uniform", n = 10, z = 4, alpha = 0.05)
```

# Interactive Visualization with the Shiny App

The package includes a Shiny application that allows users to explore the discrete‑theta Bayesian model interactively.

The app includes:

- A slider controlling the grid resolution (length.out in seq(0,1,...))
- A prior selector (Uniform or Triangular)
- A slider for α controlling the credible interval
- A table displaying the equal‑tail interval ($L,U$)
-A tri‑plot showing prior, likelihood, and posterior

# Launching the App

To run the Shiny app, we call:

```{r, fig.width=8, fig.height=5}
runCoinApp()
```

